---
title: "Intro to cstime"
output: rmarkdown::html_vignette
author: "Chi Zhang"
date: "2021-09-15"
vignette: >
  %\VignetteIndexEntry{Intro to cstime}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`cstime` provides date time functions for public health purposes.

The core functionality is consistent time conversion between :

- Date.
- Isoyear, isoweek, isoyearweek.
- Season week.

It also provides functions to generate rolling dates for computing the weekly, bi-weekly, 4 week averages. 

`cstime` is part of the [csverse](https://www.csids.no/packages.html) package suite.

```{r setup}
library(cstime)
library(magrittr)
```

To convert a date to isoyear: 

```{r}
date_to_isoyear_c('2021-01-01')
```

To convert a isoyearweek string to isoyear/isoweek: 

```{r}
isoyearweek_to_isoyear_c("2021-02")
isoyearweek_to_isoweek_c("2021-02")
```

To convert a season week to isoweek (and reverse): 

```{r}
seasonweek_to_isoweek_n(10)
isoweek_to_seasonweek_n(1)  
```
